Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-25 cordillera-cycle.tex
Update acknowledgements.

      Each simulation starts from assumed ice-free conditions at
      120\,\unit{ka}, and runs to the present.
      Our modelling domain of 1\,500 by 3\,000\,\unit{km} encompasses
      the entire area covered by the Cordilleran ice sheet at the LGM
      (Fig.~\ref{fig:locmap}). The simulations were run on two distinct
      grids, using a~lower horizontal resolution of 10\,\unit{km}, and
      a~higher horizontal resolution of 5\,\unit{km}. These computations
      were performed on 16 to 128 computing cores at the Swedish National
      Supercomputing Centre.

@@

\begin{acknowledgements}
      Foremost, we would like to thank Shawn Marshall for providing
      a~detailed, constructive analysis of this study during J.~Seguinot's
      PhD defence (September 2014). His comments were used to improve the
      model set-up. We are very thankful to Constantine Khroulev, Ed Bueler,
      and Andy Aschwanden for providing constant help and development with
      PISM. This work was supported by the Swedish Research Council~(VR)
      grant no.~2008-3449 to A.~P.~Stroeven and by the German Academic
      Exchange Service~(DAAD) grant no.~50015537 and a~Knut and Alice
      Wallenberg Foundation grant to J.~Seguinot. Computer resources were
      provided by the Swedish National Infrastructure for Computing (SNIC)
      allocation no.~2013/1-159 and~2014/1-159 to A.~P.~Stroeven at the
      National Supercomputing Center (NSC).
\end{acknowledgements}

>>>>

      Each simulation starts from assumed ice-free conditions at
      120\,\unit{ka}, and runs to the present.
      Our modelling domain of 1\,500 by 3\,000\,\unit{km} encompasses
      the entire area covered by the Cordilleran ice sheet at the LGM
      (Fig.~\ref{fig:locmap}). The simulations were run on two distinct
      grids, using a~lower horizontal resolution of 10\,\unit{km}, and
      a~higher horizontal resolution of 5\,\unit{km}.

@@

\begin{acknowledgements}
      Foremost, we would like to thank Shawn Marshall for providing
      a~detailed, constructive analysis of this study during J.~Seguinot's
      PhD defence (September 2014). His comments were used to improve the
      model set-up. We are very thankful to Constantine Khroulev, Ed Bueler,
      and Andy Aschwanden for providing constant help and development with
      PISM. We thank Shawn Marshall, Alexander Jarosch and Andrew Stumpf for
      their constructive and complementary reviews on the first manuscript.
      This work was supported by the Swedish Research Council~(VR)
      grant no.~2008-3449 to A.~P.~Stroeven and by the German Academic
      Exchange Service~(DAAD) grant no.~50015537 and a~Knut and Alice
      Wallenberg Foundation grant to J.~Seguinot. Computer resources were
      provided by the Swedish National Infrastructure for Computing (SNIC)
      allocation no.~2013/1-159 and~2014/1-159 to A.~P.~Stroeven at the
      National Supercomputing Center (NSC) and by the Swiss National
      Supercomputing Centre (CSCS) allocation no.~s573 to J.~Seguinot.
\end{acknowledgements}
